---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Indoor Air Pollution


## PRACHI JAISWAL <br>    32192673


This is a template that contains materials to create a shiny gadget application
for assessment 2. You will need the following packages installed to 
generate the gadget from this template:

```{r, eval = FALSE}
install.packages(c("shiny", "crosstalk", "plotly", "ggthemes",
                   "DT", "tidyverse", "here", "shinythemes"))
```

## How to run the app

* Load all the packages mentioned in the `README.rmd`.
* Run the libraries given in `app.R`.
* Run the app with `Run App` button given at the to right corner of `app.R`.

**NOTE:** If you face any issues, you can connect with me through [GitHub](https://github.com/pjai0005).

## Session Info


```{r session-info}
#use utils::sessionInfo() or 

sessioninfo::session_info()
```
